Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-01-10 ms/manuscript.Rmd
Add MS Word template file in style of New Phytologist

---
title: "Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes"
bibliography: "references.bib"
mainfont: Times New Roman.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Times New Roman Bold.ttf
- ItalicFont=Times New Roman Italic.ttf
- BoldItalicFont=Times New Roman Bold Italic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: newphyt.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
nocite: | 
  @Vogel1968
---

@@

<!-- FOR CONVERSION TO MS WORD ONLY: remove page numbers -->
\pagenumbering{gobble}

<!-- Set left justification (better conversion to Word than default full justification) -->
\raggedright

>>>>

---
title: "Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes"
bibliography: "references.bib"
mainfont: Times New Roman.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Times New Roman Bold.ttf
- ItalicFont=Times New Roman Italic.ttf
- BoldItalicFont=Times New Roman Bold Italic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes # need for converting tex to docx
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: new-phytologist.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
nocite: | 
  @Vogel1968
---

@@

<!-- Uncomment to remove page numbers -->
<!-- \pagenumbering{gobble}  -->

<!-- Set left justification  -->
\raggedright
